---
title: "Shiny App Presentation"
author: "Selmane Fouad"
date: "September 17, 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Synopsis

In this app, i used the NYC Taxi and Limousine Commission (TLC) to show where and when the cab drivers pick-up and drop-off their customers. The data is so big so I used the first 100 trips of the year 2016.

##Loading and processing the raw data
You can download the data from the tlc website <http://www.nyc.gov/html/tlc/html/about/trip_record_data.shtml>

```{r}
taxi<- read.csv("trips.csv")

```

The Data column names.
```{r,echo=T,comment=""}
colnames(taxi)

```

***

Her's five row of the  final data I used in my application.

```{r,comment=""}
taxi<-taxi[,c(1,7,8,11,12,3,20)]
head(taxi)
```


***

Her's the pick-up locations for 100 trips.

```{r , message=FALSE, warning=FALSE}
library(leaflet)
library(tidyr)
leaflet(taxi)%>%
  addTiles()%>%
  addMarkers(lng = taxi$lng,lat = taxi$lat)

```


